### 2018-04-29 Paper/ack.tex
..

M. Vohra and S. Mahadevan gratefully acknowledge funding support from the
National Science Foundation Award $\#$. Molecular
dynamics simulations were performed using resources at the advanced computing
center for research and education (ACCRE) at Vanderbilt University. 
M. Vohra is grateful to the ACCRE staff for their technical guidance
and support. He would also like to sincerely thank Dr. Alen Alexanderian for
insightful discussions pertaining to the derivative-based sensitivity analysis
aspect of this work.

>>>>

M. Vohra and S. Mahadevan gratefully acknowledge funding support from the
National Science Foundation (Grant No. 1404823, CDSE Program). Molecular
dynamics simulations were performed using resources at the advanced computing
center for research and education (ACCRE) at Vanderbilt University. 
M. Vohra is grateful to the ACCRE staff for their technical guidance
and support. He would also like to sincerely thank Dr. Alen Alexanderian at NC State 
University for
insightful discussions pertaining to the derivative-based sensitivity analysis
in this work.

### 2018-04-29 Paper/bayes.tex
..

As discussed earlier in Section~\ref{sec:intro}, the underlying methodology for determining the nominal 
estimates for SW potential parameters did not account for measurement error, inadequate functional
form of the potential, inherent noise in MD predictions, and parametric uncertainties. Hence, there is
a possibility of improving the estimates since using the same set of values for a wide variety of systems
and applications is not ideal. A robust approach to calibrating the parameters in the presence of
such uncertainties is made possible by using a Bayesian framework. The methodology aims at evaluating
the so-called joint posterior probability distribution (referred to as the `posterior') of the uncertain model 
parameters to be calibrated, using the Bayes' rule:

@@

\noindent where $\bm{X}$ is the set of uncertain model parameters, and $\bm{Y}$ is the available set of
experimental data i.e. bulk thermal conductivity at different temperatures in the present case. 
We exploit our findings based on sensitivity analysis in
Figure~\ref{fig:gsa} and focus on calibrating $\alpha$ and $\gamma$ i.e. $\bm{X}:\{\alpha,\gamma\}$.
$\mathcal{P}(\bm{X}\vert \bm{Y})$ is regarded as the posterior, $\mathcal{P}(\bm{Y}\vert\bm{X})$ is the
`likelihood', and $\mathcal{P}(\bm{X})$ is the joint prior probability distribution (referred to as the `prior') of $\bm{X}$.
The likelihood accounts for measurement error, and the discrepancy between experiments and model
predictions, whereas, the prior is an initial guess for the distribution of uncertain model parameters in an
interval. It also accounts for the availability of an expert opinion pertaining to their estimates. 
The posterior provides an estimate of the most likely value of the uncertain model parameters based on
prior uncertainty, experimental data used for calibration and the associated measurement error, and model
discrepancy. Additionally, the posterior is often used to quantify the uncertainty associated with model predictions. Several algorithms based on Markov chain Monte Carlo (MCMC) technique are available for  
sampling the posterior~\cite{Haario:2001, Haario:2006,Xu:2014}.

Evaluating the joint posterior of $\alpha$ and $\gamma$ using MCMC typically requires a large amount of
computational effort and is not the focus on this work. Instead, we compute and plot the joint likelihood on
a 2D cartesian grid described by $\alpha$ and $\gamma$ using Eq.~\ref{eq:like} as illustrated in
Figure~\ref{fig:like}(a). For this purpose, we consider $\alpha$ and $\gamma$ to be
independent and uniformly distributed in the intervals, [1.62,1.98] and [1.08,1.32] respectively. 
Consequently, the posterior is proportional to the likelihood, considered to be a Gaussian:

@@

\noindent where $\sigma$ is the standard deviation of the measurement error, and
$(\kappa_{\tiny{\mbox{E}}} - \kappa_{\tiny{\mbox{MD}}})$ is the discrepancy between 
NEMD predictions~($\kappa_{\tiny{\mbox{MD}}}$)
and experimental data~($\kappa_{\tiny{\mbox{E}}}$). Experimental data for $\kappa_{\tiny{\mbox{E}}}$ at 300~K
(149~W/m/K~\cite{Shanks:1963}) is used to compute the joint likelihood.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/gl}
  \\ (a)
  \begin{tabular}{cc}
  \includegraphics[width=0.50\textwidth]{./Figures/pdf_alpha}
  &
  %\hspace{3mm}
  \includegraphics[width=0.50\textwidth]{./Figures/pdf_gamma}
  \\ (b) & (c)
  \end{tabular}
\caption{(a) A joint likelihood as estimated using Eq.~\ref{eq:like} is plotted on a 2D cartesian grid
 ($\alpha\times\gamma$). Point corresponding to the maximum likelihood (MLE) is also highlighted.
 The likelihood is plotted along a line passing through MLE and parallel to the $\alpha$-axis
 in (b), and $\gamma$-axis in (c).}
\label{fig:like}
\end{center}
\end{figure}

Approximate marginal distributions for
$\alpha$ and $\gamma$ are shown in Figure~\ref{fig:like}(b) and Figure~\ref{fig:like}(c) respectively. 
It must be noted that the joint likelihood plot is essentially for the purpose of illustration. The actual posterior
should be evaluated using a substantially large set of experimental data for bulk thermal conductivity as a function
of temperature, and surrogates for NEMD predictions
need to be constructed (as discussed in Section~\ref{sec:ros}) at each temperature for which the data is made
available in order to reduce computational effort. 
The dimensionality of the surrogate could potentially be reduced a priori using DGSM and a posteriori using
Sobol sensitivity analysis as presented in this work.

>>>>

As discussed earlier in Section~\ref{sec:intro}, the underlying methodology for determining the nominal 
estimates for SW potential parameters did not account for measurement error, inadequate functional
form of the potential, inherent noise in MD predictions, and parametric uncertainties. Hence, there is
a possibility of improving the estimates since using the same set of values for a wide variety of systems
and applications is not ideal. A robust approach to calibrating the parameters in the presence of
such uncertainties is made possible by using a Bayesian framework. The methodology aims at evaluating
the so-called joint posterior probability distribution (referred to as the `posterior') of the uncertain model 
parameters to be calibrated, using Bayes' rule:

@@

\noindent where $\bm{X}$ is the set of uncertain model parameters, and $\bm{Y}$ is the available set of
experimental data i.e. bulk thermal conductivity at different temperatures in the present case. 
We exploit our findings based on sensitivity analysis in
Figure~\ref{fig:gsa} and focus on calibrating $\alpha$ and $\gamma$ i.e. $\bm{X}:\{\alpha,\gamma\}$.
$\mathcal{P}(\bm{X}\vert \bm{Y})$ is regarded as the posterior, $\mathcal{P}(\bm{Y}\vert\bm{X})$ is the
`likelihood', and $\mathcal{P}(\bm{X})$ is the joint prior probability distribution (referred to as the `prior') of $\bm{X}$.
The likelihood accounts for measurement error, and the discrepancy between experiments and model
predictions, whereas, the prior is an initial guess for the distribution of uncertain model parameters in an
interval. It also accounts for the availability of the expert opinion pertaining to their estimates. 
The posterior provides an estimate of the most likely value of the uncertain model parameters based on
prior uncertainty, experimental data used for calibration and the associated measurement error, and model
discrepancy. Additionally, the posterior is often used to quantify the uncertainty associated with model predictions. Several algorithms based on the Markov chain Monte Carlo (MCMC) technique are available for  
sampling the posterior~\cite{Haario:2001, Haario:2006,Xu:2014}.

Evaluating the joint posterior of $\alpha$ and $\gamma$ using MCMC typically requires a large amount of
computational effort and is not the focus of this work. Instead, we compute and plot the joint likelihood on
a 2D cartesian grid described by $\alpha$ and $\gamma$ using Eq.~\ref{eq:like} as illustrated in
Figure~\ref{fig:like}(a). For this purpose, we consider the priors of $\alpha$ and $\gamma$ to be
independent and uniformly distributed in the intervals, [1.62,1.98] and [1.08,1.32] respectively. 
Consequently, the posterior is proportional to the likelihood, considered to be a Gaussian:

@@

\noindent where $\sigma$ is the standard deviation of the measurement error, and
$(\kappa_{\tiny{\mbox{E}}} - \kappa_{\tiny{\mbox{MD}}})$ is the discrepancy between 
NEMD predictions~($\kappa_{\tiny{\mbox{MD}}}$)
and experimental data~($\kappa_{\tiny{\mbox{E}}}$). Experimental data for $\kappa_{\tiny{\mbox{E}}}$ at 300~K
(149~W/m/K~\cite{Shanks:1963}) is used to compute the joint likelihood. It must be noted that the likelihood
function in Eq.~\ref{eq:like} could be refined further by accounting for a model discrepancy term and hence
calibrating the associated parameters in addition to the uncertain model inputs~\cite{Kennedy:2001,Ling:2014}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/gl}
  \\ (a)
  \begin{tabular}{cc}
  \includegraphics[width=0.50\textwidth]{./Figures/pdf_alpha}
  &
  %\hspace{3mm}
  \includegraphics[width=0.50\textwidth]{./Figures/pdf_gamma}
  \\ (b) & (c)
  \end{tabular}
\caption{(a) The joint likelihood of ($\alpha$,$\gamma$) as estimated using Eq.~\ref{eq:like} is plotted
on a 2D cartesian grid. The maximum likelihood estimate (MLE) is also highlighted.
Marginal likelihoods for $\alpha$ and $\gamma$ are plotted in (b) and (c) respectively.}
\label{fig:like}
\end{center}
\end{figure}

Marginal distributions for
$\alpha$ and $\gamma$ are shown in Figure~\ref{fig:like}(b) and Figure~\ref{fig:like}(c) respectively. 
As mentioned above, the joint likelihood plot is based on the bulk thermal conductivity measurement at 300~K.
An enhanced set of experimental measurements at different bulk temperatures would help improve the
accuracy of the calibration process considering the measurement noise is not too large. Moreover, it would
help capture the correlation between calibration parameters across temperatures at which the data is
available. However, a reduced-order surrogate would be needed at each temperature in order to make the
MCMC tractable.

### 2018-04-29 Paper/cover.tex
intro pass 1 complete
..

\begin{center}
\textsc{
Facilitating Uncertainty Analysis in Non-Equilibrium Molecular Dynamics Simulations for
Thermal Transport
}

@@

Manav Vohra$^{1}$, Ali Y. Nobakht$^{2}$, Seungha Shin$^{2}$, Sankaran Mahadevan$^{1}$

>>>>

\begin{center}
\textsc{
Uncertainty Quantification in Non-Equilibrium Molecular Dynamics Simulations of
Thermal Transport
}

@@

Manav Vohra$^{1}$, Ali Yousefzadi Nobakht$^{2}$, Seungha Shin$^{2}$, Sankaran Mahadevan$^{1}$

### 2018-04-29 Paper/intro.tex
..

Classical Molecular Dynamics (MD) is commonly used to study thermal transport by means of
interactions between phonons in material systems comprising non-metallic elements such
as carbon, silicon, and germanium~\cite{Dumitrica:2010}. 
A major objective for many such studies is the
estimation of bulk thermal conductivity of the system. One of the most commonly used approach,
regarded as the direct method~\cite{Schelling:2002,Turney:2009,Zhou:2009,Landry:2009,
McGaughey:2006,Ni:2009,Shi:2009,Wang:2009,Papanikolaou:2008}, is a non-equilibrium
technique that involves the application
of a heat flux or a temperature gradient by means of thermostatting, across the system. 
Corresponding steady-state temperature gradient in the former or the heat exchange between
the two thermostats in the latter, is used to estimate the bulk thermal conductivity (at a given
length or size) using 
Fourier's law. Computations are performed for a range of system lengths and the inverse
of thermal conductivity is plotted against the inverse of length. The y-intercept of a
straight line fit to the observed trend is considered as the bulk thermal conductivity 
estimate.

Although widely used, the direct method is known to severely under-predict
the bulk thermal conductivity as compared to experimental 
measurements~\cite{Haynes:2014,Shanks:1963}. This is primarily
due to length scales used in simulation that are several orders of magnitude smaller
than those used in an experiment. As a result, the sample length is much smaller than the
bulk phonon mean free path leading to a so-called ballistic transport of the phonons.
The mean free path of such phonon modes is limited to the system size that reduces their
contribution to thermal transport. Moreover, the
introduction of thermostats typically reduces the correlation between vibrations of 
different atoms (regarded as Kapitza effect~\cite{Stevens:2007}) potentially reducing
the thermal conductivity
further~\cite{Evans:2008}. Estimation of thermal conductivity using the
direct method is therefore impacted by the choice of system size and potentially due to
variability in the thermal gradient experienced by the system due to thermostatting.

Predictions of non-equilibrium molecular dynamics (NEMD) simulations are also dependent on the
choice of the inter-atomic potential as well as values associated with individual parameters
of a given potential. For instance, in the case of crystalline Si, the Stillinger-Weber (SW)
is a widely used inter-atomic potential. However, as discussed by Stillinger and Weber
in~\cite{Stillinger:1985}, the proposed nominal values of individual parameters are based
on a limited search in the 7D parameter space while ensuring structural stability and
reasonable agreement with experiments. It is therefore likely that these nominal estimates
for individual parameter values in the SW potential may not yield accurate results for a
wide variety of Si-based systems and warrant further investigation to study the impact of
underlying uncertainties on MD predictions. Along these lines, 
a recent study by Rizzi et al. focused on the effect of
uncertainties associated with the force-field parameters on bulk water properties using MD
simulations~\cite{Rizzi:2012}. Marepalli et al. in~\cite{Marepalli:2014} considered a stochastic model
for thermal conductivity to account for inherent noise in MD simulations, and study its impact on
spatial temperature 
distribution during heat conduction. Jacobson et al. in~\cite{Jacobson:2014} implement an uncertainty
quantification framework to optimize a coarse-grained model for predicting the properties of monoatomic
 water. While these are significant contributions, it is only until recently 
that researchers have started accounting for the presence of uncertainties in MD predictions in a
systematic manner. There is a definite need for additional efforts aimed at efficiency and accuracy
to enable uncertainty analysis in MD simulations for a wide range of applications.

In the present work, we focus our efforts on uncertainty analysis in predictions of NEMD simulations
for phonon transport using a silicon bar. An overview of the set-up for the simulations is
provided in Section~\ref{sec:setup}. As discussed earlier, predictions from NEMD
exhibit large discrepancies with experimental observations depending upon system size and potentially
due to variability in the applied thermal gradient. Additionally, the thermal conductivity estimates are
tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
accomplish multiple objectives through this research effort: First, we construct response surfaces
in order to characterize the dependence of discrepancy in thermal conductivity estimates (between
MD simulations and experiments) on system size, and applied thermal gradient~(Section~\ref{sec:response}).
Second, we perform sensitivity analysis to study the impact of SW potential parameter values on 
variability in predictions~(Section~\ref{sec:sense}).
Third, we exploit our findings from sensitivity analysis to 
construct a reduced order surrogate for uncertainty analysis~(Section~\ref{sec:ros}). 
Fourth, we illustrate calibration
of the important parameters in a Bayesian setting to evaluate their posterior
distributions~(Section~\ref{sec:bayes}). Construction of the
response surfaces, parametric sensitivity analysis, and Bayesian calibration can all be computationally
challenging endeavors especially in situations involving compute-intensive simulations as in the
case of NEMD. We therefore employ polynomial chaos (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce computational effort pertaining
to the aforementioned objectives. Moreover, since the construction of a PC surrogate itself can be
expensive, we demonstrate in Section~\ref{sec:sense}, a novel approach that implements derivative-based
sensitivity measures~\cite{Sobol:2010} to a priori reduce the dimensionality of the surrogate while
ensuring reasonable predictive accuracy.

>>>>

Classical molecular dynamics (MD) is commonly used to study thermal transport by means of
phonons in material systems comprising non-metallic elements such
as carbon, silicon, and germanium~\cite{Dumitrica:2010}. 
A major objective for many such studies is the
estimation of bulk thermal conductivity of the system. One of the most commonly used approaches,
regarded as the direct method~\cite{Schelling:2002,Turney:2009,Zhou:2009,Landry:2009,
McGaughey:2006,Ni:2009,Shi:2009,Wang:2009,Papanikolaou:2008}, is a non-equilibrium
technique that involves the application
of a heat flux or a temperature gradient by means of thermostatting, across the system. 
The corresponding steady-state temperature gradient in the former or the heat exchange between
the two thermostats in the latter, is used to estimate the bulk thermal conductivity (at a given
length or size) using 
Fourier's law. However, when the simulation domain is comparable to or smaller than the
mean free path, thermal conductivity estimates from the direct method depends on the
distance between the two thermostats, due to significant contribution of boundary scattering.
Hence, to estimate the bulk thermal conductivity, computations are performed for a range of
system lengths and the inverse
of thermal conductivity is plotted against the inverse of length. The $y$-intercept of a
straight line fit to the observed trend is considered as the bulk thermal conductivity 
estimate.

Although widely used, the direct method is known to severely under-predict
the bulk thermal conductivity compared to experimental 
measurements~\cite{Haynes:2014,Shanks:1963}. This is primarily
due to length scales used in the simulation that are several orders of magnitude smaller
than those used in an experiment. As a result, the sample length is much smaller than the
bulk phonon mean free path leading to the so-called ballistic transport of the phonons.
The mean free path of such phonon modes is limited to the system size that reduces their
contribution to thermal transport. Moreover, the
introduction of thermostats typically reduces the correlation between vibrations of 
different atoms potentially reducing the thermal conductivity
further~\cite{Evans:2008}. Estimation of thermal conductivity using the
direct method is therefore impacted by the choice of system size and potentially due to
fluctuations in the thermal gradient experienced by the system due to thermostatting.

Predictions of non-equilibrium molecular dynamics (NEMD) simulations are also dependent on the
choice of the inter-atomic potential as well as values associated with individual parameters
of a given potential. For instance, in the case of crystalline Si, the Stillinger-Weber (SW)
inter-atomic potential is widely used. However, as discussed by Stillinger and Weber
in~\cite{Stillinger:1985}, their proposed nominal values of individual parameters were based
on a limited search in a 7D parameter space while ensuring structural stability and
reasonable agreement with experiments. It is therefore likely that these nominal estimates
for individual parameter values in the SW potential may not yield accurate results for a
wide variety of Si-based systems and warrant further investigation to study the impact of
underlying uncertainties on MD predictions. Along these lines, 
a recent study by Rizzi et al. focused on the effect of
uncertainties associated with the force-field parameters on bulk water properties using MD
simulations~\cite{Rizzi:2012}. Marepalli et al. in~\cite{Marepalli:2014} considered a stochastic model
for thermal conductivity to account for inherent noise in MD simulations, and study its impact on
spatial temperature 
distribution during heat conduction. Jacobson et al. in~\cite{Jacobson:2014} implemented an uncertainty
quantification framework to optimize a coarse-grained model for predicting the properties of monoatomic
 water. While these are significant contributions, it is only recently 
that researchers have started accounting for the presence of uncertainties in MD predictions in a
systematic manner. There is a definite need for additional efforts aimed at efficiency and accuracy
to enable uncertainty analysis in MD simulations for a wide range of applications.

In the present work, we focus our efforts on uncertainty analysis in the predictions of NEMD simulations
for phonon transport using a silicon bar. An overview of the set-up for the simulations is
provided in Section~\ref{sec:setup}. As discussed earlier, predictions from NEMD
exhibit large discrepancies with experimental observations depending upon system size and potentially
due to fluctuations in the applied thermal gradient. Additionally, the thermal conductivity estimates are
tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
accomplish multiple objectives through this research effort: First, we construct response surfaces
in order to characterize the dependence of discrepancy in thermal conductivity estimates (between
MD simulations and experiments) on system size, and applied thermal gradient~(Section~\ref{sec:response}).
Second, we perform sensitivity analysis to study the impact of SW potential parameter values on 
uncertainty in the predictions~(Section~\ref{sec:sense}).
Third, we exploit our findings from sensitivity analysis to 
construct a reduced order surrogate for uncertainty analysis~(Section~\ref{sec:ros}). 
Fourth, we illustrate the calibration
of important parameters in a Bayesian setting to evaluate their posterior
distributions~(Section~\ref{sec:bayes}). Construction of the
response surfaces, parametric sensitivity analysis, and Bayesian calibration can all be computationally
challenging endeavors especially in situations involving compute-intensive simulations as in the
case of NEMD. We therefore employ polynomial chaos (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce the computational effort pertaining
to the aforementioned objectives. Moreover, since the construction of a PC surrogate itself can be
expensive, we demonstrate a novel approach in Section~\ref{sec:sense} that implements derivative-based
sensitivity measures~\cite{Sobol:2010} to reduce the dimensionality of the surrogate a priori while
ensuring reasonable predictive accuracy.

### 2018-04-29 Paper/ros.tex
..

\section{Reduced Order Surrogate}
\label{sec:ros}

In this section, we focus our attention on constructing a surrogate that captures the dependence of
uncertainty in NEMD predictions for the bulk thermal conductivity ($\kappa$) on input variability
in the SW potential parameters. The surrogate is a powerful tool that greatly minimizes
the computational
effort required for forward propagation of the uncertainty from input parameters to the observable,
Sobol sensitivity analysis, and Bayesian calibration of the uncertain model parameters. Once again,
we use polynomial chaos (used to construct response surfaces for discrepancy in
Section~\ref{sec:response}) to construct the surrogate of the following functional form:

@@

As discussed earlier in Section~\ref{sec:response}, several strategies are available to
estimate the PC coefficients, $c_{\bm{s}}$. However, since the polynomial basis functions
($\Psi_{\bm{s}}(\bm{\xi}$)) are
relatively high dimensional, we use a computationally efficient approach proposed by
Blatman and Sudret to construct a PCE with sparse basis($\mathcal{A}$) using the LAR
algorithm~\cite{Blatman:2011}. Furthermore, since the NEMD simulations are compute-intensive,
estimating the PC coefficients in the 7D parameter space would still require large amount of
computational resources. Hence, we explore the possibility of reducing the dimensionality of
the surrogate. For this purpose, we 
exploit our observations in Figure~\ref{fig:ub} where a significant
jump in $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and thereby construct the 
PC surrogate in a 5D parameter space by fixing $B$ and $p$ at their nominal values. In the above
equation, $\bm{\xi}:~\{\xi_1(A),\xi_2(q),\xi_3(\alpha),\xi_4(\lambda),\xi_5(\gamma)\}$ is a set
of five canonical random variables, $\xi_i$ distributed uniformly in the interval [-1,1].
Prior intervals for the uncertain SW parameters are considered to be
$\pm~10\%$ of their respective nominal estimates except for $q$ in which case it is [0,0.1]. In
Figure~\ref{fig:loo}, we plot the leave-one-out cross-validation error 
($\epsilon_{\tiny{\mbox{LOO}}}$)~\cite{Blatman:2010}, defined
below in Eq.~\ref{eq:loo}, against the number of model realizations used to construct the 5D
PC surrogate. UQLab~\cite{Marelli:2014} was used for estimating $\epsilon_{\tiny{\mbox{LOO}}}$ and constructing
the surrogate.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_eloo}
\caption{A convergence study for the 5D PCE wherein the leave-one-out
error, $\epsilon_{\tiny{\mbox{LOO}}}$ is plotted against the number of
realizations or NEMD runs used to estimate the PC coefficients.}
\label{fig:loo}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_kde}
\caption{Comparison of bulk thermal conductivity ($\kappa$) distribution of Si based on a histogram plot
using NEMD predictions (Model) at 25 points in the 7D parameter space and a probability distribution obtained 
using kernel density estimation of  reduced order surrogate estimates of $\kappa$ for 10$^6$ samples in the 5D
parameter space.}
\label{fig:verify}
\end{center}
\end{figure}

In the second strategy, we compare NEMD
predictions and estimates from the 5D surrogate in a probabilistic sense. As shown in Figure~\ref{fig:verify}, a 
histogram plot based on the available set of NEMD predictions for bulk thermal conductivity in the 7D parameter 
space is compared with its probability distribution, obtained using the reduced order surrogate and
10$^6$ samples in the 5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$. It is observed that the probability distribution (PDF) based on estimates from the reduced order surrogate compares
favorably with the histogram. Specifically, the corresponding mode values for $\kappa$ from the two plots are
in close agreement, and the PDF reasonably captures the peaks as well as the spread in
the bulk thermal conductivity distribution as observed in the histogram. 
Hence, the reduced order surrogate is verified for accuracy in both cases. 
\bigskip

As mentioned earlier, a PC surrogate can be used to estimate Sobol global sensitivity indices in a 
straightforward manner~\cite{Sudret:2008}. Sobol first order and total effect sensitivity indices as estimated
using the reduced order surrogate and $10^{6}$ samples in the 5D parameter space are plotted using bar-graphs in
Figure~\ref{fig:gsa}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_gsa}
\caption{Sobol first-order and total effect sensitivity indices as obtained using the reduced order PC
surrogate and 10$^{6}$ samples in the 5D parameter space. }
\label{fig:gsa}
\end{center}
\end{figure}

It is found that $\kappa$ is predominantly sensitive towards the choice of $\alpha$ and
$\gamma$. This observation is consistent with our initial findings based on DGSM using 25 samples in the 7D
parameter space. However, the DGSM estimate for $\gamma$ was found to be the highest in that case. 
While sensitivity towards $A$, $q$, and $\lambda$ is observed to be comparatively less in both cases, Sobol
indices for the three parameters are estimated to be smaller by an order of magnitude compared to those
for $\alpha$ and $\gamma$. Large quantitative disagreement in parametric sensitivity between DGSM and the 
Sobol indices is however not unexpected essentially because the two metrics differ by construction.
The former is based
on an expectation of partial derivatives while the later is based on variance. Nevertheless, significant qualitative
agreement pertaining to parameter importance in the two approaches is quite encouraging. 
Moreover, verification of the reduced order
surrogate for accuracy increases our confidence in implementing DGSM to ascertain relative importance of the
SW potential parameters and hence perform uncertainty analysis for the present application with minimal
computational effort.

>>>>

\section{Reduced-order Surrogate}
\label{sec:ros}

In this section, we focus our attention on constructing a surrogate that captures the dependence of
uncertainty in NEMD predictions of the bulk thermal conductivity ($\kappa$) on input uncertainty
in the SW potential parameters. The surrogate is a powerful tool that greatly minimizes
the computational
effort required for forward propagation of the uncertainty from input parameters to the output,
Sobol\textquotesingle~sensitivity analysis, and Bayesian calibration of the uncertain model parameters. Once again,
we use polynomial chaos (used to construct response surfaces for discrepancy in
Section~\ref{sec:response}) to construct the surrogate of the following functional form:

@@

As discussed earlier in Section~\ref{sec:response}, several strategies are available to
estimate the PC coefficients, $c_{\bm{s}}$. However, since the polynomial basis functions
($\Psi_{\bm{s}}(\bm{\xi}$)) are
relatively high dimensional, we use a computationally efficient approach proposed by
Blatman and Sudret to construct a PCE with sparse basis($\mathcal{A}$) using the LAR
algorithm~\cite{Blatman:2011}. Furthermore, since the NEMD simulations are compute-intensive,
estimating the PC coefficients in the 7D parameter space would still require a large amount of
computational resources. Hence, we explore the possibility of reducing the dimensionality of
the surrogate. For this purpose, we 
exploit our observations in Figure~\ref{fig:ub} where a significant
jump in the $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and thereby construct the 
PC surrogate in a 5D parameter space by fixing $B$ and $p$ at their nominal values. In the above
equation, $\bm{\xi}:~\{\xi_1(A),\xi_2(q),\xi_3(\alpha),\xi_4(\lambda),\xi_5(\gamma)\}$ is a set
of five canonical random variables, $\xi_i$ distributed uniformly in the interval [-1,1].
Prior intervals for the uncertain SW parameters are considered to be
$\pm~10\%$ of their respective nominal estimates except for $q$ in which case it is [0,0.1]. In
Figure~\ref{fig:loo}, we plot the leave-one-out cross-validation error 
($\epsilon_{\tiny{\mbox{LOO}}}$)~\cite{Blatman:2010}, defined
below in Eq.~\ref{eq:loo}, against the number of model realizations used to construct the 5D
PC surrogate. The software, UQLab~\cite{Marelli:2014} was used for estimating $\epsilon_{\tiny{\mbox{LOO}}}$
and constructing the surrogate. The leave-one-out cross validation error ($\epsilon_{\tiny{\mbox{LOO}}}$) is
computed as:

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.65\textwidth]{./Figures/PCE5D_eloo}
\caption{A convergence study for the 5D PCE wherein the leave-one-out
error, $\epsilon_{\tiny{\mbox{LOO}}}$ is plotted against the number of
realizations or NEMD runs used to estimate the PC coefficients.}
\label{fig:loo}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_kde}
\caption{Comparison of bulk thermal conductivity ($\kappa$) distribution of Si based on a histogram plot
using NEMD predictions (Model) at 25 points in the 7D parameter space and a probability distribution obtained 
using kernel density estimation of  reduced-order surrogate estimates of $\kappa$ for 10$^6$ samples in the 5D
parameter space.}
\label{fig:verify}
\end{center}
\end{figure}

In the second strategy, we compare NEMD
predictions and estimates from the 5D surrogate in a probabilistic sense. As shown in Figure~\ref{fig:verify}, a 
histogram plot based on the available set of NEMD predictions for bulk thermal conductivity in the 7D parameter 
space is compared with its probability distribution, obtained using the reduced order surrogate and
10$^6$ samples in the 5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$. It is observed that the probability density function (PDF) based on estimates from the reduced-order surrogate compares
favorably with the histogram. Specifically, the corresponding mode values for $\kappa$ from the two plots are
in close agreement, and the PDF reasonably captures the peaks as well as the spread in
the bulk thermal conductivity distribution as observed in the histogram. 
Hence, the reduced-order surrogate is verified for accuracy in both cases. 
\bigskip

As mentioned earlier, a PC surrogate can be used to estimate the Sobol\textquotesingle~global sensitivity indices in a 
straightforward manner~\cite{Sudret:2008}. The Sobol\textquotesingle~first order and total effect sensitivity indices estimated
using the reduced-order surrogate and $10^{6}$ samples in the 5D parameter space are plotted using bar-graphs in
Figure~\ref{fig:gsa}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.65\textwidth]{./Figures/PCE5D_gsa}
\caption{Sobol\textquotesingle~first-order and total effect sensitivity indices of the SW potential parameters
w.r.t the bulk thermal
conductivity as obtained using the reduced order PC surrogate and 10$^{6}$ samples in the 5D parameter space. }
\label{fig:gsa}
\end{center}
\end{figure}

It is found that $\kappa$ is predominantly sensitive towards the choice of $\alpha$ and
$\gamma$. This observation is consistent with our initial findings based on DGSM using 25 samples in the 7D
parameter space. However, the DGSM estimate for $\gamma$ was found to be the highest in that case. 
While sensitivity towards $A$, $q$, and $\lambda$ is observed to be comparatively less in both cases, the 
Sobol\textquotesingle~indices for the three parameters are estimated to be smaller by an order of magnitude
 compared to those
for $\alpha$ and $\gamma$. Large quantitative disagreement in parametric sensitivity between DGSM and the 
Sobol\textquotesingle~indices is however not unexpected essentially because the two metrics differ by construction.
The former is based
on an expectation of partial derivatives while the later is based on variance. Nevertheless, significant qualitative
agreement pertaining to parameter importance in the two approaches is quite encouraging. 
Moreover, verification of the reduced-order
surrogate for accuracy increases our confidence in implementing DGSM to ascertain the relative importance of the
SW potential parameters and hence perform uncertainty analysis for the present application with minimal
computational effort.
